### 2013-08-21 doc/dissertation/document/chapters/spn_equations/spn_equations.tex
updating the eigenvalue verification results for spn. there was one to many digits reported

For every combination of energy group structure and solver, the
eigenvalue problem was converged with an eigensolver tolerance of
\sn{1}{-6} and a linear solver tolerance of \sn{1}{-8} in a serial
calculation. Table~\ref{tab:serial_ev_results} gives the eigenvalue
computed by each solver for each problem as well as the number of
eigenvalue iterations required to converge. For every problem, each
solver converged to the same eigenvalue within the tolerance of the
eigensolver in the same number of eigenvalue iterations.
\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lccc}\hline\hline
      \multicolumn{1}{c}{\textbf{Solver}} & 
      \multicolumn{1}{c}{\textbf{Number of Groups}} & 
      \multicolumn{1}{c}{\textbf{Iterations}} &
      \multicolumn{1}{c}{\textbf{Eigenvalue}} \\
      \hline
      BiCGStab-ILUT & 1 & 25 & 1.1059870 \\
      GMRES-ILUT & 1 & 25 & 1.1059870 \\
      MCSA-ILUT-R-C & 1 & 25 & 1.1059870 \\
      MCSA-ILUT-MR-C & 1 & 25 & 1.1059870 \\
      MCSA-ILUT-R-EV & 1 & 25 & 1.1059870 \\
      MCSA-ILUT-MR-EV & 1 & 25 & 1.1059870 \\
      \hline
      BiCGStab-ILUT & 2 & 35 & 1.1552390 \\
      GMRES-ILUT & 2 & 35 & 1.1552390 \\
      MCSA-ILUT-R-C & 2 & 35 & 1.1552390 \\
      MCSA-ILUT-MR-C & 2 & 35 & 1.1552390 \\
      MCSA-ILUT-R-EV & 2 & 35 & 1.1552390 \\
      MCSA-ILUT-MR-EV & 2 & 35 & 1.1552390 \\
      \hline
      BiCGStab-ILUT & 4 & 31 & 1.1758500 \\
      GMRES-ILUT & 4 & 31 & 1.1758500 \\
      MCSA-ILUT-R-C & 4 & 31 & 1.1758500 \\
      MCSA-ILUT-MR-C & 4 & 31 & 1.1758500 \\
      MCSA-ILUT-R-EV & 4 & 31 & 1.1758500 \\
      MCSA-ILUT-MR-EV & 4 & 31 & 1.1758500 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Serial eigensolver verification results for the
      fuel assembly problem.} \textit{Each calculation was converged
      with the same eigensolver and linear solver
      tolerances. Table~\ref{tab:spn_solver_defs} gives the
      description for each solver type presented.}}
  \label{tab:serial_ev_results}
\end{table}

>>>>

For every combination of energy group structure and solver, the
eigenvalue problem was converged with an eigensolver tolerance of
\sn{1}{-6} and a linear solver tolerance of \sn{1}{-8} in a serial
calculation. Table~\ref{tab:serial_ev_results} gives the eigenvalue
computed by each solver for each problem as well as the number of
eigenvalue iterations required to converge. For every problem, each
solver converged to the same eigenvalue within the tolerance of the
eigensolver in the same number of eigenvalue iterations.
\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lccc}\hline\hline
      \multicolumn{1}{c}{\textbf{Solver}} & 
      \multicolumn{1}{c}{\textbf{Number of Groups}} & 
      \multicolumn{1}{c}{\textbf{Iterations}} &
      \multicolumn{1}{c}{\textbf{Eigenvalue}} \\
      \hline
      BiCGStab-ILUT & 1 & 25 & 1.105987 \\
      GMRES-ILUT & 1 & 25 & 1.105987 \\
      MCSA-ILUT-R-C & 1 & 25 & 1.105987 \\
      MCSA-ILUT-MR-C & 1 & 25 & 1.105987 \\
      MCSA-ILUT-R-EV & 1 & 25 & 1.105987 \\
      MCSA-ILUT-MR-EV & 1 & 25 & 1.105987 \\
      \hline
      BiCGStab-ILUT & 2 & 35 & 1.155239 \\
      GMRES-ILUT & 2 & 35 & 1.155239 \\
      MCSA-ILUT-R-C & 2 & 35 & 1.155239 \\
      MCSA-ILUT-MR-C & 2 & 35 & 1.155239 \\
      MCSA-ILUT-R-EV & 2 & 35 & 1.155239 \\
      MCSA-ILUT-MR-EV & 2 & 35 & 1.155239 \\
      \hline
      BiCGStab-ILUT & 4 & 31 & 1.175850 \\
      GMRES-ILUT & 4 & 31 & 1.175850 \\
      MCSA-ILUT-R-C & 4 & 31 & 1.175850 \\
      MCSA-ILUT-MR-C & 4 & 31 & 1.175850 \\
      MCSA-ILUT-R-EV & 4 & 31 & 1.175850 \\
      MCSA-ILUT-MR-EV & 4 & 31 & 1.175850 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Serial eigensolver verification results for the
      fuel assembly problem.} \textit{Each calculation was converged
      with the same eigensolver and linear solver
      tolerances. Table~\ref{tab:spn_solver_defs} gives the
      description for each solver type presented.}}
  \label{tab:serial_ev_results}
\end{table}
